Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-11-03 draft.tex
sec 8.1,2,3

Before stating the definition of this model, we introduce the following variants of the de Rham complex of differential forms on $\RR_{\geq 0}$ and compactly supported differential forms.

Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
\[
\{f \in  C^{\infty}(\RR_{\geq 0}) \; | \; f(0) = 0\}  \xto{\d_{\rm dR}} \Omega^1(\RR_{\geq 0})[-1]  .
\]
Notice that this is a subcomplex of the full de Rham complex on $\RR_{\geq 0}$.
In fact, this is a de Rham model for the relative cohomology of the pair $(\RR_{\geq 0}, \partial \RR_{\geq 0} = \{t = 0\})$.

Similarly, let $\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) \subset \Omega^{\bu}_{c}(\RR_{\geq 0})$ be the subcomplex of compactly supported de Rham forms on $\RR_{\geq 0}$ whose zero form component vanishes at $t = 0$.

Notice that $\Tilde{\Omega}_c^\bu(\RR_{\geq 0})$ (and $\Tilde{\Omega}^\bu_c(\RR_{\geq 0})$) admits the obvious enhancement to a sheaf (cosheaf) of commutative dg algebras on $\RR_{\geq 0}$.

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the constructible factorization algebra on $M \times \RR_{\geq 0}$ where
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg), 
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}([0,\epsilon))[2] \right) \bigg).
\]
%\brian{this is wrong
%\[
%\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
%\]
%}
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
i : U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}([0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}([0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V') \Hat{\otimes} \Tilde{\Omega}^{\bu}_{c}([0,\epsilon'))[2] \right) \bigg).
\end{tikzcd}
\]
%\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
%\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
%\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
The first map uses the fact that the symmetric algebra functor is symmetric monoidal. 
The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding~(\ref{eqn:embed}). 
\end{dfn}

\begin{rmk}
For an open $U \subset M \times \RR_{>0}$, pulling back along an embedding $\iota : U \hookrightarrow V \times [0,\epsilon)$ determines a composition of cochain complexes
\[
\Omega^\bu (V') \otimes \Tilde{\Omega}^\bu([0,\epsilon)) \xto{j^*}  \Omega^\bu (V') \Hat{\otimes} \Omega^\bu((0,\epsilon)) \cong \Omega^\bu(V \times (0,\epsilon)) \xto{\iota^*} \Omega^\bu(U) .
\]
This composition provides the version of restriction $\iota^*$ of de Rham forms used in the definition above.
\end{rmk}

@@

Next, we define the $\PP_0$-bracket for the value of the factorization algebra on open sets of the form $V \times [0,\epsilon)$. 
Notice that the underlying graded vector space of $\bC_n(\fg)(V \times [0,\epsilon))$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V) \otimes \Tilde{\Omega}^\bu ([0,\epsilon))) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2] \right) \right)  .
\]
We first define the bracket $\{F,G\}$ between the following simple elements 
\[
F : \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \to k
\]
and 
\[
G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon))[2] .
\]
Define $\{F, G\}$ by the composition
\[
\begin{tikzcd}
k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
\bigg(\fg \otimes \Omega^\bu_c(V) \Hat{\otimes} \Tilde{\Omega}^{\bu}_{c}([0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot] \otimes \wedge}"] \\
& \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
\end{tikzcd}
\]
The middle bracket is induced from the Lie bracket on $\fg$ and the wedge product of differential forms.
Again, this bracket is extended to the full algebra by the Leibniz rule.
\end{proof}

@@

Recall that for $V \subset M$ we have
\[
\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}(\RR_{\geq 0})[2] \right) \bigg) .
\]
On $V$, the map $I^\partial$ is defined by the composition
\[
\begin{tikzcd}
\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}(\RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \times \Omega^\bu_c (V)[1] \right) .
\end{tikzcd}
\]
The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$. 
It is quick to check that $I^{\partial}$ extends to a map of factorization algebras.

@@

It is the central theme of \cite{CG1, CG2} that the observables of a {\em perturbative} field theory define the structure of a factorization algebra. 
Moreover, the observables are equipped with the structure of a $\PP_0$ factorization algebra.

@@

\begin{dfn}
Let $M$ be an $n$-dimensional manifold and let $\fg$ be an $L_\infty$ algebra. 
{\em Topological BF theory with its universal Neumann boundary condition} is the classical BV theory on $M \times \RR_{\geq 0}$ described by the following constructible sheaf $\cL$ of $L_\infty$ algebras:
\begin{itemize}
\item[(1)] 
The bulk theory is perturbative topological BF theory on $M \times \RR_{>0}$. 
That is, to an open set $U \subset M \times \RR_{>0}$ the theory is described by the $L_\infty$ algebra 
\[
\cL (U) = \Omega^{\bu} (U) \otimes \fg [1] \ltimes \Omega^{\bu} (U) \otimes \fg^* [n-3] .
\]
\item[(2)] 
To an open set $V \times [0,\epsilon)$, we assign the $L_\infty$ algebra
\[
\cL (V \times [0,\epsilon)) = \Omega^\bu (V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \otimes \fg \ltimes \Omega^{\bu} (V \times [0,\epsilon)) \otimes \fg^* [n-3] .
\]
\end{itemize}
\end{dfn}

@@

\begin{proof}
\brian{all we need to say is that half-smeared is equivalent to full observables}

%Suppose $V \times [0,\epsilon) \subset M \times \RR_{\geq 0}$ is an open set. 
%Then, as cochain complexes 
%\[
%\clie^\bu(\cL(V \times [0,\epsilon)) = {\rm Sym} \left(\Bar{\Omega}^\bu_c(V \times [0,\epsilon) [2] \right)  .
%\]
%Here $\Bar{\Omega}^\bu_c$ denotes the compactly supported distributional de Rham forms. 
%By ellipticity, the inclusion $\Omega^\bu \hookrightarrow \Bar{\Omega}^\bu_c$ is a quasi-isomorphism which induces a quasi-isomorphism
%\[
%\bC_n(\fg) (V \times [0,\epsilon)) \hookrightarrow \clie^\bu(\cL(V \times [0,\epsilon)) 
%\]
%as desired. 
%The quasi-isomorphism for the value of the factorization algebras on open sets $U \subset M \times \RR_{>0}$ is defined similarly. 
\end{proof}

@@

In the ordinary Batalin--Vilkovisky formalism on manifolds without boundary it is the central theme of \cite{CG2} that to any effective family of functionals satisfying the ``quantum master equation'' one can associate a factorization algebra of quantum observables.
On manifolds with boundary, this approach appears in the work of Rabinovich \cite{EugeneNew}.
We expect that one can exhibit our constructible factorization algebra as the quantum factorization algebra of observables associated to a Batalin--Vilkovisky quantization of BF theory on $M \times \RR_{\geq 0}$.

@@

\begin{rmk} Examples

Poisson $\sigma$-model. 
$B$-model. 
cite paper with Eugene.
Kapustin-Witten. 
\end{rmk}

>>>>

Before stating the definition of this model, we introduce the following variants of the de Rham complex of differential forms on manifolds with boundary.

Suppose $N$ is a manifold with boundary and denote by $i_\partial : \partial N \hookrightarrow N$ the boundary embedding.
Let $\Omega^{\bu}(N \, | \, \partial N)$ be the subcomplex of de Rham forms $\alpha$ on $N$ with the property that $i_\partial^* \alpha  = 0$.
For instance, if $N = \RR_{\geq 0}$, then $\Omega^{\bu}(\RR_{\geq 0} \, | \, \{0\})$ is equal to the two-term complex
\[
  \{f \in  C^{\infty}(\RR_{\geq 0}) \; | \; f(0) = 0\}  \xto{\d_{\rm dR}} \Omega^1(\RR_{\geq 0})[-1]  .
\]
The complex $\Omega^\bu(N \, | \, \partial N)$ is a de Rham model for the relative cohomology of the pair $(N, \partial N)$.

Similarly, let $\Omega^{\bu}_{c}(N \, | \, \partial N)$ be the subcomplex of compactly supported de Rham forms $\alpha$ on $N$ with the property that $i_\partial^* \alpha = 0$.

Notice that both $\Omega^\bu(N \, | \, \partial N)$ and its compactly supported version are commutative dg subalgebras of the full de Rham complex.

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the constructible factorization algebra on $M \times \RR_{\geq 0}$ where
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg), 
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
    \bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V)  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) \, | \, V) [2] \right) \bigg)
\]
%\brian{this is wrong
%\[
%\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
%\]
%}
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
i : U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V) \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) \, | \, V)[2] \right) \bigg) \ar[d, "\simeq"] \\
\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V \times [0,\epsilon) \, | \, V \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V \times [0,\epsilon) \, | \, V) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
\clies\bigg(\fg \otimes \Omega^\bu(V' \times [0,\epsilon') \, | \, V')  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V' \times [0,\epsilon') \, | \, V') [2] \right) \bigg).
\end{tikzcd}
\]
%\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
%\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
%\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
The first map uses the fact that the symmetric algebra functor is symmetric monoidal. 
The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding~(\ref{eqn:embed}). 
\end{dfn}

\begin{rmk}
For an open $U \subset M \times \RR_{>0}$, pulling back along an embedding $\iota : U \hookrightarrow V \times [0,\epsilon)$ determines a composition of cochain complexes
\[
  \Omega^\bu (V \times [0,\epsilon) \, | \, V) \xto{j^*}  \Omega^\bu (V \times (0,\epsilon)) \xto{\iota^*} \Omega^\bu(U)
\]
where $j : V \times (0,\epsilon) \hookrightarrow V \times [0,\epsilon)$ is the open embedding.
This composition provides the version of restriction $\iota^*$ of de Rham forms used in the definition above.
\end{rmk}

@@

Next, we define the $\PP_0$-bracket for the value of the factorization algebra on open sets of the form $V \times [0,\epsilon)$. 
Notice that the underlying graded vector space of $\bC_n(\fg)(V \times [0,\epsilon))$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V \times [0,\epsilon) \, | \, V) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon) \, | \, V) [2] \right) \right)  .
\]
We first define the bracket $\{F,G\}$ between the following simple elements 
\[
F : \fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V) [2] \to k
\]
and 
\[
G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon) \, | \, V)[2] .
\]
Define $\{F, G\}$ by the composition
\[
\begin{tikzcd}
k \otimes \bigg(\fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] &
\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon) \, | \, V) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V)\bigg)
\ar[d,"{[\cdot, \cdot] \otimes \wedge}"] \\
& \fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V) [2] \ar[d, "F"] \\ & k
\end{tikzcd}
\]
The middle bracket is induced from the Lie bracket on $\fg$ and the wedge product of differential forms.
Again, this bracket is extended to the full algebra by the Leibniz rule.
\end{proof}

@@

Recall that for $V \subset M$ we have
\[
  \bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V \times \RR_{\geq 0} \, | \, V) \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0} \, | \, V)[2] \right) \bigg) .
\]
On $V$, the map $I^\partial$ is defined by the composition
\[
\begin{tikzcd}
  \clies\bigg((\fg \otimes \Omega^\bu(V \times \RR_{\geq 0} \, | \, V) \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0} \, | V)[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
\end{tikzcd}
\]
The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V \times \RR_{\geq 0} \, | \, V)[1]\right)$ and the second map is induced by integration along $\RR_{\geq 0}$.
It is quick to check that $I^{\partial}$ extends to a map of factorization algebras.

@@

It is the central theme of \cite{CG1, CG2} that the observables of a {\em perturbative} field theory define the structure of a factorization algebra.
The value of the factorization algebra on an open set $U$ is, by definition, the functionals on the fields restricted to $U$.
Furthermore, the observables are equipped with the structure of a $\PP_0$ factorization algebra.

@@

\begin{dfn}
Let $M$ be an $n$-dimensional manifold and let $\fg$ be an $L_\infty$ algebra. 
{\em Topological BF theory with its universal Neumann boundary condition} is the classical BV theory on $M \times \RR_{\geq 0}$ described by the following constructible sheaf $\cL$ of $L_\infty$ algebras:
\begin{itemize}
\item[(1)] 
The bulk theory is perturbative topological BF theory on $M \times \RR_{>0}$. 
That is, to an open set $U \subset M \times \RR_{>0}$ the theory is described by the $L_\infty$ algebra 
\[
\cL (U) = \Omega^{\bu} (U) \otimes \fg [1] \ltimes \Omega^{\bu} (U) \otimes \fg^* [n-3] .
\]
\item[(2)] 
To an open set $V \times [0,\epsilon)$, we assign the $L_\infty$ algebra
\[
    \cL (V \times [0,\epsilon)) = \Omega^\bu (V \times [0,\epsilon) \, | \, V) \otimes \fg \ltimes \Omega^{\bu} (V \times [0,\epsilon)) \otimes \fg^* [n-3] .
\]
\end{itemize}
\end{dfn}

@@

\begin{proof}
  This proposition follows by tracing through some definitions, together with a key fact in functional analysis.

  First, observe that the cochain complex which is {\em linear dual}\footnote{Here, we mean continuous linear dual, taking into account the structure of de Rham forms as a topological vector space.} to the cochain complex $\Omega^\bu (V \times [0,\epsilon)) \otimes \fg^*[n-3]$ is
  \[
    \Bar{\Omega}_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2].
  \]
  Here, the bar in $\Bar{\Omega}_c$ indicates compactly supported distributional differential forms.
  In words, this is the space of compactly supported distributional de Rham forms $\alpha$ valued in $\fg[2]$ with the property that $i_\partial^* \alpha = 0$.
  Where, as above, $i_\partial : \partial N \hookrightarrow N$ is the boundary embedding.

  Now, there is a natural inclusion of cochain complexes of the smooth (non-distributional) compactly supported de Rham forms inside of the distributional ones:
  \begin{equation}\label{eqn:AB}
    \Omega_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2]\Bar{\Omega}_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2] .
  \end{equation}
  Furthermore, using ellipticity of the de Rham operator we can assert by the Atiyah--Bott lemma \cite{??} that this inclusion is a quasi-isomorphism.

  With this bit of functional analysis out of the way, we observe that the value of the factorization algebra $\clies(\cL)$ on $V \times [0,\epsilon)$ is

  The value of $\clies(\cL)$ on an open set $U$ is
  \[
    \clies\bigg(\fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V)  \; , \; \Sym\left(\fg \otimes \Bar{\Omega}^\bu_c (V \times [0,\epsilon) \, | \, V) [2] \right) \bigg) .
\]
So, the quasi-isomorphism (\ref{eqn:AB}) induces a quasi-isomorphism
\[
  \bC_n(\fg)(V \times [0,\epsilon)) \xto{\simeq} \clies(\cL)(V \times [0,\epsilon)) .
\]

Checking that $\bC_n(\fg)(U) \to \clies(\cL)(U)$ for open sets of the form $U \subset M \times \RR_{>0}$ is completely similar.
%Suppose $V \times [0,\epsilon) \subset M \times \RR_{\geq 0}$ is an open set. 
%Then, as cochain complexes 
%\[
%\clie^\bu(\cL(V \times [0,\epsilon)) = {\rm Sym} \left(\Bar{\Omega}^\bu_c(V \times [0,\epsilon) [2] \right)  .
%\]
%Here $\Bar{\Omega}^\bu_c$ denotes the compactly supported distributional de Rham forms. 
%By ellipticity, the inclusion $\Omega^\bu \hookrightarrow \Bar{\Omega}^\bu_c$ is a quasi-isomorphism which induces a quasi-isomorphism
%\[
%\bC_n(\fg) (V \times [0,\epsilon)) \hookrightarrow \clie^\bu(\cL(V \times [0,\epsilon)) 
%\]
%as desired. 
%The quasi-isomorphism for the value of the factorization algebras on open sets $U \subset M \times \RR_{>0}$ is defined similarly. 
\end{proof}

@@

In the ordinary Batalin--Vilkovisky formalism, on manifolds without boundary, it is the central result of \cite{CG2} that to any effective family of functionals satisfying the ``quantum master equation'' one can associate a factorization algebra of quantum observables.
For manifolds with boundary, this has been developed in the work of Rabinovich \cite{EugeneNew}.
We expect that one can exhibit our constructible factorization algebra as the quantum factorization algebra of observables associated to a Batalin--Vilkovisky quantization of BF theory on $M \times \RR_{\geq 0}$.

@@

%\begin{rmk} Examples
%Poisson $\sigma$-model.
%$B$-model.
%cite paper with Eugene.
%Kapustin-Witten.
%\end{rmk}
